---
title: "p8105_hw1_jc4166"
author: "Jerri Chen"  
date: "2019_09-16"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 1
Create a data frame comprised of the following:  

* a random sample of size 8 from a standard Normal distribution  
* a logical vector indicating whether elements of the sample are greater than 0  
* a character vector of length 8  
* a factor vector of length 8, with 3 different factor “levels”  

```{r problem1}

problem1_df = tibble(
  norm_samp = rnorm(8),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("My", "name", "is", "Jerri", "Chen", "MD", "PhD", "MS"),
  vec_factor = factor(c("A", "B", "C", "A", "B", "C", "A", "B"))
)
```

Take the mean of each variable in the problem1_df.

* The mean of the numeric variable is `r mean(pull(problem1_df, norm_samp))`.
* The mean of the logical variable is `r mean(pull(problem1_df, norm_samp_pos))`.
* The mean of the character variable is `r mean(pull(problem1_df, vec_char))`.
* The mean of the factor variable is `r mean(pull(problem1_df, vec_factor))`.

I am unable to take the mean of the character or vector variable because they are not numeric.

The following code chunk demonstrates the as.numeric function on the variables from problem1_df.

```{r, eval = FALSE}
problem1_numeric_df = tibble(
  norm_samp = rnorm(8),
  norm_samp_pos = as.numeric(norm_samp > 0),
  vec_char = as.numeric(c("My", "name", "is", "Jerri", "Chen", "MD", "PhD", "MS")),
  vec_factor = as.numeric(factor(c("A", "B", "C", "A", "B", "C", "A", "B")))
)
```

The following code chunk demonstrates conversion and nested conversion of logical variables from problem1_df, with column cross products.

```{r, eval = FALSE}
problem1_convert_df = tibble(
  norm_samp = rnorm(8),
  norm_samp_pos_numeric = as.numeric(norm_samp > 0),
  Product1 = norm_samp*norm_samp_pos_numeric,
  norm_samp_pos_factor = as.factor(norm_samp > 0),
  Product2 = norm_samp*norm_samp_pos_factor,
  norm_samp_pos_factor_num = as.numeric(as.factor(norm_samp > 0)),
  Product3 = norm_samp*norm_samp_pos_factor_num
)
```

## Problem 2
Create a data frame comprised of the following:  

* x: a random sample of size 500 from a standard Normal distribution  
* y: a random sample of size 500 from a standard Normal distribution  
* A logical vector indicating whether x + y > 1  
* A numeric vector created by coercing the above logical vector  
* A factor vector created by coercing the above logical vector  

```{r problem2}
problem2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  sum_xy1 = x + y > 1,
  sum_xy1_numeric = as.numeric(x + y > 1),
  sum_xy1_factor = as.factor(sum_xy1_numeric)
)
```

* The number of rows is `r nrow(problem2_df)`.
* The number of columns is `r ncol(problem2_df)`.
* The mean of x is `r mean(pull(problem2_df, x))`.
* The median of x is `r median(pull(problem2_df, x))`.
* The standard deviation of x is `r sd(pull(problem2_df, x))`.
* The proportion of cases for which x + y > 1 is `r sum(pull(problem2_df, sum_xy1)) / length(pull(problem2_df, sum_xy1))`.

Scatter plot adding color using logical variable:
```{r yx_scatter1}
ggplot(problem2_df, aes(x = x, y = y, color = sum_xy1)) + geom_point()
```

Scatter plot adding color using numeric variable:
```{r yx_scatter2}
ggplot(problem2_df, aes(x = x, y = y, color = sum_xy1_numeric)) + geom_point()
```

Scatter plot adding color using factor variable:
```{r yx_scatter3}
ggplot(problem2_df, aes(x = x, y = y, color = sum_xy1_factor)) + geom_point()
```
